Eleven years of student replication projects provide evidence on the correlates of replicability in psychology

### 2023-04-29 paper/manuscript.Rmd
smoothed out results a little

PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.  During the 10 week class, students replicated a published finding. They individually re-implemented the study, wrote analysis code, pre-registered their study, collected data using an online platform, and wrote up a structured replication report. Students were free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science. The resultant sample of studies is not a random sample from the literature but is representative of studies that are of interest to and doable by first year graduate students.

@@

Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020]. Because we operationalized replicability as whether a study could support cumulative science, we used a subjective rating of replication success as our primary outcome measure. This measure was applicable across the diverse range of statistical measures and reporting practices present in the sample. It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest. A holistic measure of replication success had been coded for each project when it was turned in at the end of the class. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (`r round(pluck(matching,2,1)/176*100)`% of cases).

As a complement, we also used two statistical measures of replication on the subset of the data where they were computable (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021]. These both measure how similar the outcome estimates from the two sets of data are.

@@

<!-- VERONICA IS HERE IN GOING BACK THROUGH --> 
## Overall replication rate

@@

Across the 176 studies, the overall subjective replication rate was `r round(pluck(sub_rep_rate,1))`%. `r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of the studies had replication outcomes within the prediction interval of the original outcome. The median p_original value was `r round(pluck(porig_rate, 1),2)`. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero. On average, there is a diminution of effect sizes from original to replication.

@@

## Single predictors
Properties of both the original study and the replication can influence whether or not the replication is a success. We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication was. A full description of these features is given in Methods.

Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, higher numbers of trials, and the original study having open data. Predictors of lower replicability included single vignetted studies, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at `r round(1/subfield, 2)` times the rate of social psychology studies. Within and between subjects designs were both common, and within-subjects designs replicated `r within |> round(2)` times as much. Similarly, studies with multiple vignettes replicated `r round(1/vignette, 2)` times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield. Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.

Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).  While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

@@

## Regression model
While a number of predictors show individual correlations with the subjective replication score, many of the predictors also correlate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models). We ran models both using all the data, but without statistical predictors (that were uncodable for some studies) and models including statistical predictors, but limiting to the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients. The general directions of coefficients are consistent with the effects of the predictors in isolation.

@@

# Discussion
Prior large scale replications of psychology findings have estimated the replication rate at somewhere around 50%. This rate feels low, raising the question of what is causing so many studies not to replicate. However, limited numbers of replications and limited research into specific predictors of replication failure leave this an open question.

@@

Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we looked at whether similar enough results could be obtained under the resource, expertise, and time constraints on early stage graduate students. We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand. Other replication projects have estimated replicabilty in other circumstances; for instance, @camerer2018 looks at likely studies are to replicate when performed by an expert with a large budget, and @ebersole2020 asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.

Replication results should be interpreted in light of their methods and estimand. We do not interpret our non-replications as indicating the original studies were false positives (presumably some were and some weren't). There are many possible reasons for the non-replications in this sample. In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study. When these issues are diagnosed, they suggest possible ways to "rescue" the replication by fixing power or encouraging participants to take the task seriously, without altering the underlying experiment. In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample. That said, not all scientists notice the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed. In many non-replication cases, it was unclear why the results failed to replicate.

We also caution in the interpretation of our predictor variables.  Some of the correlates are most easily interpreted as being about the original study, and others seem to be more about the closeness of the replication to the original. This was a correlational design, so we cannot attribute causality to any of these factors. For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design. Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.

>>>>

PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.  During the 10 week class, each student replicated a published finding. They individually re-implemented the study, wrote analysis code, pre-registered their study, collected data using an online platform, and wrote up a structured replication report. Students were free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science. The resultant sample of studies is not a random sample from the literature but is representative of studies that are of interest to and doable by first year graduate students.

@@

Many different measures can be used to define replication success of an individual statistical result [@simonsohn2015; @gelman2018; @mathur2020]. However, a single test of a single statistical result doesn't capture the sense of whether a replication is close enough that one could feel confident extending the finding, so we used a subjective rating of replication success as our primary outcome measure.  This subjective measure, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample. Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class. For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (`r round(pluck(matching,2,1)/176*100)`% of cases).

As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}). We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic [@errington2021]. These both measure how similar the outcome estimates from the two sets of data are.

@@

## Overall replication rate

@@

Across the 176 studies, the overall subjective replication rate was `r round(pluck(sub_rep_rate,1))`%. `r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of the studies had replication outcomes within the prediction interval of the original outcome. The median p_original value was `r round(pluck(porig_rate, 1),2)`. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero. On average, there was a diminution of effect sizes from original to replication.

@@

## Single predictors
We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability. We chose a set of predictor variables based on the correlational results of RP:P [@openscienceconsortium2015], our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was. A full description of these features is given in Methods.

Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, larger numbers of trials, and the original study having open data. Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated at `r round(1/subfield, 2)` times the rate of social psychology studies. Within and between subjects designs were both common, and within-subjects designs replicated `r within |> round(2)` times as much. Studies with multiple vignettes replicated `r round(1/vignette, 2)` times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield.

Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data. Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).  While online studies in general show comparable results to studies conducted in person [@crump2013], switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (ex. inductions may be weaker or attention checks inadequate to the new sample). These factors of open materials, open data, and online samples in original studies are more common in more recent studies, and so these effects may partially reflect temporal trends.

@@

## Regression model

While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models). We ran models both using all the data, but without statistical predictors (that were uncodable for some studies) and models including statistical predictors, but limiting to the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization. The general directions of coefficients are consistent with the effects of the predictors in isolation.

@@

# Discussioni

MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
Prior large scale replications of psychology findings have estimated the replication rate at somewhere around one half, which intuitively feels low. However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.

@@

Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we considered whether results similar to the original could be obtained under the resource, expertise, and time constraints on early stage graduate students. We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand. Other replication projects have estimated replicabilty in other circumstances; for instance, @camerer2018 looks at how likely studies are to replicate when performed by an expert with a large budget, and @ebersole2020 asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.

Replication results should be interpreted in light of their methods and estimand. We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't). There are many possible reasons for the non-replications in this sample. In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study. When these issues are diagnosed, they suggest possible ways to "rescue" the replication by increasing the sample or changing the interface, without altering the underlying experiment. In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample. That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed. In many non-replication cases, it was unclear why the results failed to replicate.

We also caution the interpretation of our predictor variables.  Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original. This was a correlational design, so we cannot attribute causality to any of these factors. For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design. Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.

### 2023-04-29 paper/manuscript.tex
smoothed out results a little

Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). Because we operationalized replicability as whether a study could support cumulative science, we used a subjective rating of replication success as our primary outcome measure. This measure was applicable across the diverse range of statistical measures and reporting practices present in the sample. It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest. A holistic measure of replication success had been coded for each project when it was turned in at the end of the class. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (26\% of cases).

As a complement, we also used two statistical measures of replication on the subset of the data where they were computable (136 cases, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al. 2021}). These both measure how similar the outcome estimates from the two sets of data are.

@@

Across the 176 studies, the overall subjective replication rate was 49\%. 45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome. The median p\_original value was 0.03. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero. On average, there is a diminution of effect sizes from original to replication.

@@

Properties of both the original study and the replication can influence whether or not the replication is a success. We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication was. A full description of these features is given in Methods.

Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, higher numbers of trials, and the original study having open data. Predictors of lower replicability included single vignetted studies, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies. Within and between subjects designs were both common, and within-subjects designs replicated 3.35 times as much. Similarly, studies with multiple vignettes replicated 2.62 times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield. Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.

Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person). While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al. 2013}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

@@

While a number of predictors show individual correlations with the subjective replication score, many of the predictors also correlate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models). We ran models both using all the data, but without statistical predictors (that were uncodable for some studies) and models including statistical predictors, but limiting to the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients. The general directions of coefficients are consistent with the effects of the predictors in isolation.

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Prior large scale replications of psychology findings have estimated the replication rate at somewhere around 50\%. This rate feels low, raising the question of what is causing so many studies not to replicate. However, limited numbers of replications and limited research into specific predictors of replication failure leave this an open question.

@@

Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we looked at whether similar enough results could be obtained under the resource, expertise, and time constraints on early stage graduate students. We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand. Other replication projects have estimated replicabilty in other circumstances; for instance, Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) looks at likely studies are to replicate when performed by an expert with a large budget, and Ebersole et al. (\protect\hyperlink{ref-ebersole2020}{2020}) asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.

Replication results should be interpreted in light of their methods and estimand. We do not interpret our non-replications as indicating the original studies were false positives (presumably some were and some weren't). There are many possible reasons for the non-replications in this sample. In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study. When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by fixing power or encouraging participants to take the task seriously, without altering the underlying experiment. In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample. That said, not all scientists notice the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed. In many non-replication cases, it was unclear why the results failed to replicate.

We also caution in the interpretation of our predictor variables. Some of the correlates are most easily interpreted as being about the original study, and others seem to be more about the closeness of the replication to the original. This was a correlational design, so we cannot attribute causality to any of these factors. For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design. Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.

>>>>

Many different measures can be used to define replication success of an individual statistical result (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). However, a single test of a single statistical result doesn't capture the sense of whether a replication is close enough that one could feel confident extending the finding, so we used a subjective rating of replication success as our primary outcome measure. This subjective measure, unlike statistical measures, accommodated studies with multiple important outcome measures that together defined the pattern of interest and was applicable across the diverse range of statistical measures and reporting practices present in the sample. Importantly, a holistic measure of replication success had already been coded for most projects when they were turned in at the end of the class. For reliability, VB independently code the replication success from the students' written reports; discrepancies were resolved by discussion between MCF and VB (26\% of cases).

As a complement to our primary subjective outcome, we also used two statistical measures of replication on the subset of the data where they were computable for the key statistic of interest (136 cases, see Figure \ref{fig:prisma}). We used p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, and prediction interval, a binary measure of whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al. 2021}). These both measure how similar the outcome estimates from the two sets of data are.

@@

Across the 176 studies, the overall subjective replication rate was 49\%. 45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome. The median p\_original value was 0.03. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero. On average, there was a diminution of effect sizes from original to replication.

@@

We investigated what features of the original study and replication were correlated with replication success, with the goal of being able to identify potential markers of replicability. We chose a set of predictor variables based on the correlational results of RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}), our own intuitions of experimental design factors that might impact replication success, and some covariates related to how close the replication was. A full description of these features is given in Methods.

Many predictors individually correlate with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, larger numbers of trials, and the original study having open data. Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented in the replication sample, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies. Within and between subjects designs were both common, and within-subjects designs replicated 3.35 times as much. Studies with multiple vignettes replicated 2.62 times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield.

Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data. Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person). While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al. 2013}), switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well-adapted (ex. inductions may be weaker or attention checks inadequate to the new sample). These factors of open materials, open data, and online samples in original studies are more common in more recent studies, and so these effects may partially reflect temporal trends.

@@

While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models). We ran models both using all the data, but without statistical predictors (that were uncodable for some studies) and models including statistical predictors, but limiting to the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization. The general directions of coefficients are consistent with the effects of the predictors in isolation.

@@

\hypertarget{discussioni}{%
\section{Discussioni}\label{discussioni}}

MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
Prior large scale replications of psychology findings have estimated the replication rate at somewhere around one half, which intuitively feels low. However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.

@@

Our metric of replicability was operationalized around the idea of whether a study could support cumulative science, so we considered whether results similar to the original could be obtained under the resource, expertise, and time constraints on early stage graduate students. We think this is a valuable estimand that is consistent with scientists' reasons for valuing replicability, but it is not the only estimand. Other replication projects have estimated replicabilty in other circumstances; for instance, Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) looks at how likely studies are to replicate when performed by an expert with a large budget, and Ebersole et al. (\protect\hyperlink{ref-ebersole2020}{2020}) asks how likely certain studies are to replicate when performed with extensive feedback from the original authors.

Replication results should be interpreted in light of their methods and estimand. We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't). There are many possible reasons for the non-replications in this sample. In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study. When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by increasing the sample or changing the interface, without altering the underlying experiment. In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample. That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed. In many non-replication cases, it was unclear why the results failed to replicate.

We also caution the interpretation of our predictor variables. Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original. This was a correlational design, so we cannot attribute causality to any of these factors. For instance, while within-subjects designs are more likely to replicate than between-subjects designs, this could be related to power, or the types of experiments that tend to be run in each design. Given the predictive value, slightly more skepticism and critical reading of between-subjects designs may be warranted, but this correlation, by itself, does not mean scientists should prefer to run within-subjects designs.
